---
title: "Tablet app metadata"
author: "Rick O. Gilmore"
date: "January 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preliminaries

Data were stored in .xml files on Adolph lab server within participant-specific folders. These are now copied to a local set of directories:

`analysis/data/xml`

## Opening a sample XML file

```{r packages, echo=TRUE, results='hide'}

# Install package to work with XML files if needed
# install.packages("XML")

# Then load into current space
library("XML")


# Surround in () to print variable
(xml.file <- xmlParse(file = "analysis/data/xml/Phone Home Questionnaires 20160929_2016-10-03_10-52-44.xml"))
xml.top <- xmlRoot(xml.file) # grabs top node
```

It looks like we have the following overall structure:

```
<Combined_Questionnaires>
  <phone_questionnaire>
    Infant characteristics
    Mom characteristics
    Family characteristics
  <home_questionnaire>
    Locomotor milestones
    MacArthur
    Media Use
    Rothbart ECBQ
    Home environment
```

I suspect that we will want separate data files for each of the questionnaire measures and a single file with the demographic data collected during the phone questionnaire.

### Phone questionnaire data

```{r phone-quest, echo=TRUE, results='hide'}
xml.top[[5]] # gives data from <phone_questionnaire>
```

### Home questionnaire data

```{r home-quest, echo=TRUE, results='hide'}
xml.top[[6]] # gives <home_questionnaire data>

xml.top[[6]][[2]] # gives sex and test date
xml.top[[6]][[3]] # gives child exact age and agegroup
xml.top[[6]][[4]] # gives date of child's 6 mo birthday, 5:24 generate similar
                 # dates up to 24 mos
xml.top[[6]][[23]] # footwear data

xml.top[[6]][[25]] # loc_milestones_walk
xml.top[[6]][[26]] # walk_onset_mos

xml.top[[6]][[28]] # loc_milestones_crawl
xml.top[[6]][[29]] # crawl_onset_mos

xml.top[[6]][[32]] # macarthur_2_e

xml.top[[6]][[33]] # media_use_p1
xml.top[[6]][[34]] # media_use_p2
xml.top[[6]][[35]] # media_use_p3
xml.top[[6]][[36]] # media_use_p4

xml.top[[6]][[37]] # Rothbart ECBQ

xml.top[[6]][[38]] # HOME environment
```